Product plots

### 2011-06-23 prodplots-infovis.tex
Label graphics with f syntax

  \caption{Plots of the distribution of happiness and sex (\key{male} male, \key{female} female).}
  \label{fig:fact-simple}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{part-marital-1}%
    \includegraphics[width=0.5\linewidth]{part-marital-2}
  \caption{(Left) The joint distribution of marital status and age (in decades) partitioned by a vspine and hspine.  (Right) The joint distribution of age and marital status partitioned by a vspine and hbar.}
  \label{fig:marital}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{wt-count}%
    \includegraphics[width=0.5\linewidth]{wt-wtssall}%
  \caption{Joint distribution of age and sex (\key{male} male, \key{female} female). (Left) counts and (right) probability weights. In this case, there is very little difference between the plots.}
  \label{fig:weighting}
\end{figure}

@@

  \caption{The distribution of happiness with age. (Left) hbar + vspine: an extension of the histogram. (Right) hspine + vspine: an extension of the spinogram.}
  \label{fig:cont-examples}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{sex-marital-happy}%
    \includegraphics[width=0.5\linewidth]{cascade}
  \caption{A mosaic plot of happiness by marital status and sex. (Left) Coloured by happiness (\key{not-too-happy} Not too happy, \key{pretty-happy} pretty happy, \key{very-happy} very happy).  (Right) A cascaded view helps show how the plot is built up.}
  \label{fig:cascade}
\end{figure}

>>>>

  \caption{Plots of the distribution of happiness and sex (\key{male} male, \key{female} female) (Left) $f(happy)$, (Middle) $f(sex | happy)$, (Right) $f(happy, sex)$.}
  \label{fig:fact-simple}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{part-marital-1}%
    \includegraphics[width=0.5\linewidth]{part-marital-2}
  \caption{(Left) The joint distribution of marital status and age, $f(marital, age)$, (in decades) partitioned by a vspine and hspine.  (Right) The joint distribution of age and marital status, $f(age, marital)$, partitioned by a vspine and hbar.}
  \label{fig:marital}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{wt-count}%
    \includegraphics[width=0.5\linewidth]{wt-wtssall}%
  \caption{Joint distribution of age and sex (\key{male} male, \key{female} female), $f(age, sex)$. (Left) counts and (right) probability weights. In this case, there is very little difference between the plots.}
  \label{fig:weighting}
\end{figure}

@@

  \caption{The distribution of happiness with age, $f(age, happy)$. (Left) hbar + vspine: an extension of the histogram. (Right) hspine + vspine: an extension of the spinogram.}
  \label{fig:cont-examples}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{sex-marital-happy}%
    \includegraphics[width=0.5\linewidth]{cascade}
  \caption{A mosaic plot of happiness by marital status and sex, $f(happy, marital, sex)$. (Left) Coloured by happiness (\key{not-too-happy} Not too happy, \key{pretty-happy} pretty happy, \key{very-happy} very happy).  (Right) A cascaded view helps show how the plot is built up.}
  \label{fig:cascade}
\end{figure}
